### 2018-07-23 express2018/conclusions.tex
More on future work

For the future work, it would be worth extending the current work
to multi-variable equations/contractions, with other equivalences
and preorders considered, notably the trace-related relations.
On the other side, one could examine the formalisation of a different approach to unique
solutions, in which the use of contraction is
replaced by semantic conditions on process transitions such as
divergence. \cite{DurierHS17}

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas Tuerk.

% The second half of this
% paper was written in memory of  Mike J. Gordon.

>>>>

For the future work, it would be worth extending the current work
to multi-variable equations/contractions, with other equivalences
and preorders considered, notably the trace-related relations.
On the other side, one could examine the formalisation of a different
approach \cite{DurierHS17} to unique
solutions, in which the use of contraction is
replaced by semantic conditions on process transitions such as
divergence. \hl{The problem of formalising value-passing CCS in a
more elegant way with minimal efforts (by exploiting the type variable
of actions, for example) also deserves some thinking.}

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas Tuerk.
%
The second half of this
paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.
